%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.21in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}

%\documentclass{article}
\usepackage{booktabs}% http://ctan.org/pkg/booktabs


\newcommand{\tabitem}{~~\llap{\textbullet}~~}


\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Darshil Saraiya}{}%{Last update on \today }

\nobreakvspace{0.4em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:sdarshil22.at.gmail.dot.com}{sdarshil22\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller{+}1 (408)821-9681\sbull
{\newnums \href{https://github.com/darshilsaraiya}{darshilsaraiya (Github)}\sbull
{\mewmums \href{https://www.linkedin.com/in/darshilsaraiya/}{www.linkedin.com/in/darshilsaraiya}\sbull
{\mewmums {California}
\\
{%San Jose\sbull
%CA%\sbull
%95112\sbull
%United States
}


\spacedhrule{0.0em}{-0.4em}
\roottitle{Experience}



\headedsection  % sets the header for the section and includes any subsections
  {Sony Interactive Entertainment LLC}
  {\textsc{California, United States}} {%
  \headedsubsection
    {Software Intern (Project: Kubernetes Development)}
    {June \apo17 -- August \apo17}
    {\bodytext
    {
    \begin{itemize}
        \item Worked in DevOps Team to build capacity management for kubernetes cluster system using Prometheus. 
        \item Developed REST APIs in Node.js for reporting system and Containerized Node.js application.
        \item Technologies: Kubernetes, Prometheus, Docker, NodeJS-Express, Docker Trusted Registry.
    \end{itemize}}}
}

\headedsection  % sets the header for the section and includes any subsections
  {Kloud.io}
  {\textsc{California, United States}} {%
  \headedsubsection
    {Software Engineer Intern (Project: Integration Platform as a Service)}
    {March \apo17 -- April \apo17}
    {\bodytext
    {
    \begin{itemize}
        \item Developed REST APIs for invoicing using Stripe billing and invoicing system for the product.
        \item Implemented Cron jobs using Node.js Cron library.
        \item Technologies: NodeJS-Express, AWS S3, PostgreSQL, MySQL, MSSQL, Oracle DB, AWS RDS, Cron library, Stripe APIs
    \end{itemize}}}
}

\headedsection  % sets the header for the section and includes any subsections
  {eSecure Software}
  {\textsc{Ahmedabad, India}} {%
  \headedsubsection
    {Graduate Trainee (Project: Web Application Development)}
    {January \apo15 -- December \apo15}
    {\bodytext
    {
    \begin{itemize}
        \item Created Web services for various features in NodeJS-Express framework.
        \item Designed and Implemented front-end of the Web Application
        \item Technologies: NodeJS-Express, AngularJS, MongoDB
    \end{itemize}}}
}

\spacedhrule{0.0em}{-0.4em}



%\spacedhrule{0.0em}{-0.4em}

%spacedhrule{0.0em}{-0.4em}



\roottitle{Academic Projects}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://github.com/darshilsaraiya/Amazon}{Amazon Fresh Prototype}
  \textbf{
  \small{(NodeJS - Express | AngularJS | MongoDB | MySQL | RabbitMQ | Redis | Mocha | Jmeter | Bootstrap | AWS)}}}
  {} {%
  
    {\bodytext
    {
    \begin{itemize}
        \item Implemented a 3-tier web application which includes user, farmer and admin functionalities.
        \item Provided functionalities like sign-up, sign-in with Password Encryption, give order, add-update-delete products-farmers-users, products as well as farmer search with Connection Pooling, load balancer and lazy loading.
    \end{itemize}}}
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://github.com/darshilsaraiya/dockmate}{DockMate - Self-Adaptive Elastic Docker Cloud for Web-based applications}
  \textbf{
  \small{(Docker | Docker-Compose | HA Proxy Load Balancer | Java | Socket-IO | Google Compute Engine)}}}
  {} {%
  
    {\bodytext
    {
    \begin{itemize}
        \item Designed an elastic cloud for web applications using multiple Docker containers. Implemented dynamic provisioning/release of docker containers as per actual load.
        \item Developed a monitoring system which monitors and predicts traffic for next interval based on HTTP request rate and resource utilization. The system dynamically scales in/out required docker containers with web application.
    \end{itemize}}}
}


\headedsection  % sets the header for the section and includes any subsections
  {\href{https://github.com/darshilsaraiya/LibraryManagementSystem}{Library Management System}
  \textbf{
  \small{(Spring MVC | Java | JPA | AWS RDS | AWS EC2 | Google Books API)}}}
  {} {%
  
    {\bodytext
    {
    \begin{itemize}
        \item Built a 3-tier web application which manages library system, including cataloguing, search, circulation, waiting list.
        \item Developed an app for two users - Librarian and Patron with the integration of Google Books API.
        
    \end{itemize}}}
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://github.com/darshilsaraiya/SparkScalaAllPairsSimilarity}{Scaling Similarity Search for Big Data}
  \textbf{
  \small{(Apach Spark | Amazon S3 | Amazon EMR | Amazon EFS | Haddop YARN )}}}
  {} {%
  
    {\bodytext
    {
    \begin{itemize}
        \item Implemented the Spark driver program in order to enable an algorithm to run on multi-node cluster. This cluster is deployed in Amazon EMR.
        \item Created Amazon S3 buckets and Amazon EFS to store the output of similarity search and metadata storage.
        \item Gained 3.6 to 12.4 speedup by using spark driver. The speedup is measured in time required to calculate the similarity.
        
    \end{itemize}}}
}


\spacedhrule{0.0em}{-0.4em}

\roottitle{Skills}
{\bodytext{
  \begin{tabular}{ll}
    %\midrule
    \tabitem \textbf{Programming Languages} & Java, C++, Android, Scala, Python \\[.1\normalbaselineskip]
    \tabitem \textbf{Web Technologies} & Javascript, NodeJS-Express, JAX-WS, AJAX, Spring, Rest Web-Services \\[.1\normalbaselineskip]
    \tabitem \textbf{Front-end Technologies} & Html 5, CSS, AngularJs, Bootstrap, XML \\[.1\normalbaselineskip]
    \tabitem \textbf{Databases/Middleware} & MySQL, MS SQL, MongoDB, AWS RDS, Oracle, RabbitMQ, Redis \\[.1\normalbaselineskip]
    \tabitem \textbf{Testing Tools and Frameworks} \hspace{.3cm}  &  JMeter, JUnit, Mocha, Selenium \\[.1\normalbaselineskip]
    \tabitem \textbf{Operating Systems} & Unix, Linux, Mac, Windows \\[.1\normalbaselineskip]
    \tabitem \textbf{Cloud Technologies} & Kubernetes, Docker, AWS, Google Cloud Platform, IBM Bluemix \\[.1\normalbaselineskip]
    \tabitem \textbf{Cluster Computing} & Apache Spark \\[.1\normalbaselineskip]
    \tabitem \textbf{Monitoring Tools} & Prometheus \\[.1\normalbaselineskip]
    \tabitem \textbf{SCM and Versioning Tools} & Git, Gradle, Maven, Intellij, Eclipse \\[.1\normalbaselineskip]
  \end{tabular}
}}


\spacedhrule{0.0em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{http://www.sjsu.edu/}{San Jose State University} }
  {\textsc{California, United States}} {%
  \headedsubsection
    {Master of Science in Software Engineering}
    {Graduated - December \apo17}
    {}
}


\headedsection
  {\href{http://ddu.ac.in}{Dharmsinh Desai University} }
  {\textsc{Gujarat, India}} {%
  \headedsubsection
    {Bachelor of Technology in Computer Engineering}
    {Graduated - May \apo14}
    {}
}

\end{document}
\documentclass[oneside]{book}
